Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-22 paper/structureScene.tex
definition of x_2
define wavelet on the log-frequency axis
place fig 1

\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}

@@

@@

>>>>

\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}

@@

\begin{figure}
\begin{center}
\setlength{\unitlength}{1cm}
\begin{picture}(5,2)
 \put(-1.5,0.0){\includegraphics[height=2cm,width=3.5cm]{gammatone_Q8.png}}
 \put(2.5,0.0){\includegraphics[height=2cm,width=3.5cm]{gammatone_Q1.png}}
\end{picture}
\caption{
Left: Gammatone wavelet $\boldsymbol{\psi_{\gamma_1}}(t)$ with a quality factor of $Q_1=8$.
Right: Gammatone wavelet $\boldsymbol{\psi_{\gamma_2}}(t)$ with a quality factor of $Q_2=1$.}
\end{center}
\end{figure}

@@

\begin{equation}
\boldsymbol{\psi_{\gamma_{\mathrm{fr}}, \theta_{\mathrm{fr}}}}(\gamma_1)
= \theta_{\mathrm{fr}} 2^{-\gamma_{\mathrm{fr}}/Q_{\mathrm{fr}}}
\boldsymbol{\psi_{\theta_{\mathrm{fr}}}}( \theta_{\mathrm{fr}}  2^{-\gamma_{\mathrm{fr}}/Q_{\mathrm{fr}}}\gamma_1)
\end{equation}

\begin{equation}
\boldsymbol{x_2}(t,\gamma_1,\gamma_2,\gamma_{\mathrm{fr}},\theta_{\mathrm{fr}}) =
\vert \boldsymbol{x_1}
\overset{t}{\ast} \boldsymbol{\psi_{\gamma_2}}
\overset{\gamma_1}{\ast} \boldsymbol{\psi_{\gamma_{\mathrm{fr}}, \theta_{\mathrm{fr}}}}
\vert (t,\gamma_1)
\end{equation}
Again, we use the generic literal $\gamma$ as a shorthand for $\gamma_1$ or $(\gamma_1, \gamma_2, \gamma_{\mathrm{fr}}, \theta_{\mathrm{fr}})$.
